SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Convert code cells to executable cells
Fix code errors and add imports

```python
class Decay(System):
    x: Variable = initial(default=1)  # Variable with initial condition
    eq = x.derive() << -x  # equation assigning dx/dt = -x
```

@@

```python
class Oscillator(System):
    x: Variable = initial(default=1)
    v: Derivative = x.derive(initial=0)
    eq = v.derive() << -x
```

@@

```python
class BigModel(System):
    x: Variable = initial(default=1)
    subsystem = Oscillator(x=x)
    independent = Oscillator(x=1)  # independent variable created inside
```

@@

```python
class Model(System):
    k: Constant = assign(default=1, constant=True)
    # two variables sharing initial condition
    x: Variable = initial(default=c)
    y: Variable = initial(default=c)

@@

```python
sim = Simulator(Oscillator)
df = sim.solve(save_at=np.linspace(0, 5, 100))

@@

```python
df.plot()
```

@@

```python
class Model(Copmartment):
    """2A -> B"""
    A: Species = initial(default=1)
    B: Species = initial(default=0)
    r = Reaction(reactants=[2 * A], product=[B], rate=1)
```

>>>>

```{python}
from poincare import Variable, System, initial

class Decay(System):
    x: Variable = initial(default=1)  # Variable with initial condition
    eq = x.derive() << -x  # equation assigning dx/dt = -x
```

@@

```{python}
from poincare import Derivative

class Oscillator(System):
    x: Variable = initial(default=1)
    v: Derivative = x.derive(initial=0)
    eq = v.derive() << -x
```

@@

```{python}
class BigModel(System):
    x: Variable = initial(default=1)
    subsystem = Decay(x=x)
    independent = Decay(x=1)  # independent variable created inside
```

@@

```{python}
from poincare import Constant, Parameter, assign

class Model(System):
    c: Constant = assign(default=1, constant=True)
    # two variables sharing initial condition
    x: Variable = initial(default=c)
    y: Variable = initial(default=c)

@@

```{python}
import numpy as np
from poincare import Simulator

sim = Simulator(Oscillator)
df = sim.solve(save_at=np.linspace(0, 5, 101))

@@

```{python}
df.plot();
```

@@

```{python}
from simbio import Compartment, Species, Reaction, initial

class Model(Compartment):
    """2A -> B"""
    A: Species = initial(default=1)
    B: Species = initial(default=0)
    r = Reaction(reactants=[2 * A], products=[B], rate_law=1)
```
